Model Checking Differentially Private Properties

### 2018-01-30 introduction.tex
intro organisation done

An important byproduct of this work is to analyze privacy over
infinite behaviors. Consider the formula $\dpriv{\epsilon}{\delta}
(\G \F \mathit{high})$. A state satisfies the formula if it
is probabilistically similar to always almost surely\lz{infinitely often}
answer $\mathit{high}$ as similar states. Compared to the unbounded
but finite behavior specified by $\F \mathit{high}$,
$\G \F \mathit{high}$ specifies an infinite behavior.
Not only can differential privacy specify randomized algorithms, it
also naturally generalizes to reactive systems.
Privacy analysis applies to systems with infinite behaviors as well.

@@

\paragraph{Contributions.} Our main contributions are three folds. (i)
We introduce the logic $\dpCTLstar$ for reasoning about properties in
differential privacy. We use the logic to express classical
differential privacy properties, and moreover, complex properties such as those
involving infinite behaviors can also be expressed. (ii) We model several differential privacy mechanisms, including the streaming process, in Markov chains or Markov decision processes.
(iii) We show that the model checking problem
problem for Markov chains is standard. For MDPs we show that it is undecidable.

>>>>

An important byproduct of this work is to analyze privacy over
infinite behaviors. Consider the formula $\dpriv{\epsilon}{\delta}
(\G \F \mathit{high})$. A state satisfies the formula if it
is probabilistically similar to  infinitely often
answer $\mathit{high}$ as similar states. Compared to the unbounded
but finite behavior specified by $\F \mathit{high}$,
$\G \F \mathit{high}$ specifies an infinite behavior.
Not only can differential privacy specify randomized algorithms, it
also naturally generalizes to reactive systems.
Privacy analysis applies to systems with infinite behaviors as well.

@@

\paragraph{Contributions.} Our main contributions are threefold. (I)
We introduce the logic $\dpCTLstar$ for reasoning about properties in
differential privacy. We use the logic to express classical
differential privacy properties, and moreover, complex properties such as those
involving infinite behaviors can also be expressed. (II) We model several differential privacy mechanisms, including the streaming process, in Markov chains or Markov decision processes.
(III) We show that the model checking problem
problem for Markov chains is standard. For MDPs we show that it is undecidable.

### 2018-01-30 main.tex
proof appendix
work through and 16 pages ;)
adaptions
intro organisation done

\title{Model Checking Differentially Private Properties}
\ifpublic
\author{
Depeng Liu\inst{1}
\and
Bow-Yaw Wang\inst{2}
\and
Lijun Zhang\inst{1}}
\institute{
Chinese Academy of Sciences
\and
Academia Sinica
}
\else
\author{\vspace*{-1.2cm}}
\institute{\vspace*{-1.2cm}\ }
\fi

@@

This paper is organized as follows. After the introduction,
preliminaries are given in Section~\ref{section:preliminaries}. The
logic $\dpCTL$ is presented in
Section~\ref{section:dpCTL}. The model cheking algorithms are developed in
Section~\ref{section:model-checking-algorithms}. They are followed by
applications (Section~\ref{section:applications}. Finally,
Section~\ref{section:conclusions} concludes our presentation.

@@

>>>>

\title{Model Checking Differentially Private Properties}
\ifpublic
\author{
Depeng Liu\inst{1}
\and
Bow-Yaw Wang\inst{2}
\and
Lijun Zhang\inst{1}}
\institute{
Chinese Academy of Sciences
\and
Academia Sinica
}
\else
\author{Author}
\institute{Institute}
\fi

@@

\paragraph{Organisation of the paper.}
Preliminaries are given in Section~\ref{section:preliminaries}. 
In Section~\ref{section:examples} we discuss how differential privacy mechanisms can be modeled in Markov chains.
The logic $\dpCTLstar$ and model checking algorithms for Markov chains are presented in
Section~\ref{section:dpCTL}. 
Section~\ref{section:specifying-properties} describes differential privacy properties using   $\dpCTLstar$.
They are followed by the extension to Markov decision processes and an
application in streaming process (Section~\ref{section:mdp}). Finally,
Section~\ref{section:conclusions} concludes our presentation.

@@

\newpage
\appendix

\section{Proof of Theorem~\ref{theorem:mdp-model-checking}}
\input{proof}
